Chaotic mixing of tidal debris

### 2015-06-21 ms.tex
references and more text about potentials

noise in hamiltonian systems: \citep{kandrup00}

@@

Time dependence of the Galactic potential is difficult to include generically. While, for example, the spherically average mass profile of a dark matter halo may evolve predictably \citep[in cosmological simulations;][]{wechsler02, buist14}, the global shape may change due to accretion and phase-mixing of subhalos, bulk rotation, or collapse. Over the last $\approx$6 Gyr, however, the Milky Way may have had a relatively calm accretion history and therefore these effects may not be important. In future work we will explore the effect of steady mass-accretion on the orbit structure of more complex potentials

[discussion of potential choice?]
Why not disk + bulge? What do we expect when we add?

Real disk will be self-consistent with halo, so this isn't really a fair test, but still...

Other effects: radial dependence of axis ratios, time dependence, etc.

@@

\acknowledgements
The authors wish to thank Robyn Sanderson, Dan D'Orazio, David Merritt, and the \emph{Stream Team} for useful comments and discussion.
APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}.
This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance.

>>>>

Cosmological simulations predict that dark matter halos are filled with substructure in the form of dark matter subhalos. If they exist, these subhalos may account for up to $\approx$1-10\% of the mass of the dark matter \citep{??} and therefore may contribute significantly to and orbit in the large-scale potential of any galaxy. Gravitational scattering due to subhalo interactions has been studied, however in the halos of galaxies where dynamical times are long, the scattering cross-section for \emph{strong} encounters is very small \citep{??}. Instead, the collective effect of the subhalos may instead act as a noise term in the Hamiltonian of any halo orbit. This subhalo-induced colored noise --- which depends on the mass spectrum and distribution of subhalos --- may also act to simply increase the magnitude of chaos along orbits, and destabilize sufficiently non-resonant orbits \citep[see, e.g.,][]{kandrup00}.

@@

Galaxies are certainly not static systems. To first order, galaxies grow in mass --- for example, the spherically averaged mass profile of dark matter halos evolves fairly predictably in cosmological simulations \citep{wechsler02, buist14} after some initial period of stochastic mass growth. The Milky Way has probably had a fairly calm accretion history over the last 6 Gyr and therefore the mass growth may be similar to that seen in simulations. This steady growth most likely does not alter the global structure or shape of the potential. However, we also know from simulations that figure rotation, baryonic feedback, and the accretion and phase-mixing of subhalos do perturb the global state of simulated halos. \cite{deibel11} showed that by adopting pattern speeds comparable to those found in cosmological simulations, figure rotation generally acts to destabilize orbits (rather than stabilize chaotic orbits in the equivalent static potential) and the resulting orbit structure is that most regular orbits are associated with resonances. In future work we will explore the effect of these time-dependent processes on the chaotic dispersal of tidal streams using live potentials from cosmological N-body simulations.

@@

\acknowledgements
The authors wish to thank Robyn Sanderson, Dan D'Orazio, David Merritt, and the \emph{Stream Team} for useful comments and discussion. APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. This research made use of \project{Astropy}, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}. This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance.
